%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.5in,right=0.6in,bottom=0.5in]{geometry} % Document margins
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.5}
\hypersetup{colorlinks,breaklinks,linkcolor=black,urlcolor=black,anchorcolor=darkblue,citecolor=darkblue}

\usepackage{amsmath,scalerel}
\DeclareMathOperator*{\Bigcdot}{\scalerel*{\cdot}{\bigodot}}

\name{Richard Knoche} % Your name

\address{(703)-801-4456 \\ \href{mailto: raknoche@gmail.com\\}
{raknoche@gmail.com}} % Your phone number and email
\address{ \href{www.dealingdata.net}{www.dealingdata.net} \\ \href{http://www.linkedin.com/in/richardknoche}{www.linkedin.com/in/richardknoche} }% Your phone number and email
\address{Greater New York City} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\hspace{-1em} {\bf University of Maryland, College Park} \hfill {Aug 2011 - Dec 2016} \\ 
Doctor of Philosophy in Physics \\
Dissertation: Signal Corrections and Calibrations in the LUX Dark Matter Detector

\hspace{-1em} {\bf James Madison University} \hfill {Aug 2007 - May 2011} \\ 
Bachelor of Science in Physics, magna cum laude \\

\vspace{-1em}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Insight Data Science}{Data Science Fellow}{Jan 2017 - Present}{}{ }
\item Consulted for AptDeco.com to quantify the subjective quality of half a million user-uploaded images.
\item Implemented 60 hand-crafted image features in a Python-based AdaBoost random forest classifier to automatically identify high-quality and low-quality images with 73\%  and 68\% accuracy, respectively.
\item The classifier will improve editor efficiency by 40\%, and save an estimated \$45,000 annually.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of Maryland}{Graduate Research Assitant}{May 2011 - Dec 2016}{}{ }

\item Worked with an international collaboration to produce upper limits on dark matter interaction rates.
\item Developed analysis techniques to remove over 99.9\% of background signals from our data. These techniques have been adopted by experiments in the USA, Asia, and Europe.
\item Implemented maximum likelihood estimation in Python and MATLAB to produce signal corrections and improve our detector's sensitivity by an order of magnitude.
\item Automated the extraction of hundreds of data features from 650 TB of data.  Maintained these features in a MySQL database that was queried by 200 collaborators.


\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{NASA GSFC}{Research Assistant}{June 2010 - Sep 2010}{}{}
\item Performed exploratory and statistical analysis of data from the Swift Burst Alert Telescope (BAT) to search for hard X-ray emissions around the on-set time of supernovae.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PERSONAL PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Personal Projects}

\begin{rSubsection}{DealingData.net}{Data Science Blog}{Jul 2016 - Present}{}
\item Predicted the top fantasy football performers of each season with a support vector machine ($R^2=0.72$).  Used K-means clustering to automatically extract tiers of players to target during a fantasy draft. 
\item Implemented a Naive Bayes sentiment analysis on Pokemon Go tweets from each state.  Used the results to measure the dominance of each team across the country. Visualized the results in an interactive map. 
\item Presented in-depth tutorials on various topics, including time series analysis, statistical analysis of correlated variables, Bayesian statistics, specific APIs, web scraping, and web hosting.
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{8ex}} l }
Computer Languages & Python (Sklearn, SciPy, Pandas, Gensim, Flask), MATLAB, HTML \\
Quantitative Skills & Physics, Calculus, Profile Likelihood, Error Analysis, Monte Carlo \\
Machine Learning & MLE, Linear Regression, Naive Bayes, Random Forest, Logistic Regression, \\
 & TF-IDF, Association Rules, K-means \\
Tools & SVN, Git, MySQL \\
\end{tabular}


\end{rSection}


\end{document}
