% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,MMMyyyy,nonstop]{simpleresumecv}
% Class options:
% a4paper, letterpaper, draft, nonstop
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Richard Knoche}
\newcommand{\CVTitle}{Richard Knoche's CV}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{http://www.dealingdata.net}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
\href{https://www.google.com/maps/place/8810+62nd+Ave,+Berwyn+Heights,+MD+20740/@38.995313,-76.908195,17z/data=!3m1!4b1!4m5!3m4!1s0x89b7c3fd69c6911b:0xa23453a69afa6fc8!8m2!3d38.995313!4d-76.908195}
{8810 62nd Ave, Berwyn Heights, Maryland 20740, USA}
\par
\href{mailto:raknoche@gmail.com}
{raknoche@gmail.com}
\,\SubBulletSymbol\,
(703)\,801-4456
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\CVWebpage}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Experience}
{Experience}
{PDF:ResearchExperience}

\href{http://umdphysics.umd.edu/}
{\textbf{University of Maryland}},
Physics Department

\GapNoBreak
\BulletItem
Graduate Research Assistant
\hfill
\DatestampY{2011} -- Present

\begin{detail}
\SubBulletItem
Developed ground breaking techniques that produced the world's most accurate and most precise calibrations of a dark matter detector.
\SubBulletItem
Created position dependent signal corrections that improved detector performance.
\SubBulletItem
Automated the extraction of hundreds of data features from calibration data.
\SubBulletItem
Directed on-site detector operations as Deputy Science Coordination Manager.
\SubBulletItem
Responsible for monitoring system status and responding to alarm conditions as Detector Operations Manager.
\end{detail}

\BigGap
\href{http://csma31.csm.jmu.edu/physics/}
{\textbf{National Aeronautics and Space Administration}},
Goddard Space Flight Center

\GapNoBreak
\BulletItem
Research Assistant
\hfill
\DatestampY{2010}

\begin{detail}
\SubBulletItem
Analyzed data from Swift Burst Alert Telescope (BAT) to search for hard X-ray emissions around the on-set time of supernovae.
\SubBulletItem
Quantified the X-ray counterpart to Fermi-LAT pulsar observations using X-ray emission data from the Chandra and BeppoSax missions.
\end{detail}

\BigGap
\href{http://csma31.csm.jmu.edu/physics/}
{\textbf{James Madison University}},
Physics Department

\GapNoBreak
\BulletItem
Undergraduate Research Assistant
\hfill
\DatestampY{2008} --
\DatestampY{2011}
\begin{detail}
\SubBulletItem
Designed and maintained table-top experiments to characterize the complex, non-linear behavior of granular systems.
\SubBulletItem
Implemented computer vision techniques to quantitatively characterize particle movement in a two dimensional shear flow.
\SubBulletItem
Utilized optical polarization techniques to quantify stress networks in granular systems.
\SubBulletItem
Performed statistical analysis to characterize relevant parameters in a two dimensional granular shear flow.
\end{detail}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{http://umd.edu/}
{\textbf{University of Maryland}},
College Park, Maryland, USA

\GapNoBreak
\BulletItem
Doctor of Philosophy (Ph.D.) in
\href{http://umdphysics.umd.edu/}
{Physics}
\hfill
\DatestampYM{2011}{08}--
\DatestampY{2016 (Expected)}
\begin{detail}
\SubBulletItem
Thesis:
\href{http://updatethis}
{Signal Corrections and Calibrations in the LUX Dark Matter Detector}
\end{detail}


\BigGap
\href{http://www.jmu.edu/}
{\textbf{James Madison University}},
Harrisonburg, Virginia, USA

\GapNoBreak
\BulletItem
Bachelor of Science (B.S.) in
\href{http://csma31.csm.jmu.edu/physics/}
{Physics}, magna cum laude
\hfill
\DatestampYM{2007}{08} --
\DatestampYM{2011}{05}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

\Gap
\begin{tabular}{llll}
Physics & Mathematics & Data Analysis & Statistics\\
Matlab & Python & C++ & MySQL\\
HTML & CSS & Bash & Git \\
Machine Learning & Machining & 
\end{tabular}

%%%%%%%%%%%%
%% Honors %%
%%%%%%%%%%%%

%Section: Honors
\section
{Honors}
{Honors}
{PDF:Honors}
\textbf{John Mather Nobel Scholar Award}
\hfill
\DatestampYM{2010}{08}
\BulletItem
Awarded for high academic achievement, and contributions to research at NASA's Goddard Space Flight Center.  Funded by money from John Mather's Nobel Prize in physics.


\textbf{Henry W. Leap Scholarship}
\hfill
\DatestampYM{2010}{03}
\BulletItem
Awarded to one student each year for academic excellence and significant research contributions.

\textbf{Sigma Pi Sigma Inductance}
\hfill
\DatestampYM{2010}{03}
\BulletItem
Accepted into the national physics honors society.

\textbf{President's List, James Madison Univesity}
\hfill
\DatestampY{2009} -- 
\DatestampY{2011} 
\BulletItem
Awarded for academic excellence (3.9 GPA or higher).  Received this honor every semester from Fall 2009 until graduation in Spring 2011.

\textbf{Dean's List, James Madison Univesity}
\hfill
\DatestampY{2008} --
\DatestampY{2011} 
\BulletItem
Awarded for academic excellence (3.5 GPA or higher).  Received this honor every semester from Fall 2008 until graduation in Spring 2011.

\BigGap
\Gap
\textbf{ References and publications available upon request}
\end{body}

\end{document}
